Surrogate model of aligned-spin binary neutron star waveforms using Gaussian process regression

### 2017-10-03 paper/paper.tex

Let us now discuss the construction of the full waveform. The Hamiltonian equations of motion with the above radiation-reaction force are numerically integrated beginning with the quasicircular initial conditions described in Ref.~\cite{Buonanno:2005xu}. The inspiral-plunge waveform is obtained by evaluating Eq.~(\ref{hlminspplunge}) using the solution to the orbital dynamics. Let $\Omega$ be the instantaneous orbital frequency, $r$ be orbital separation, $p_r$ be the radial momentum, $f_s$ be the waveform sampling frequency in Hz, $\omega_{\textrm{peak}}^{\textrm{NR}}$ be the NR fit for the (2,2)-mode amplitude peak of a BNS merger defined in Eq.~(2) of Ref.~\cite{Bernuzzi:2015rla}~\footnote{Note that this fit was tuned to NR simulations only for $0 \leq \kappa_2^T \leq 500$, where $\kappa_2^T$ is defined by Eq.~(1) of Ref.~\cite{Bernuzzi:2015rla}. In our model, for $\kappa_2^T >500$ we use the value of this fit at $\kappa_2^T=500$.}. Then the numerical integration of the orbital dynamics stops when any of the following events happens: (i) $\Omega$ peaks, (ii) $p_r$ becomes positive, (iii) $\dot{r}$ becomes positive, (iv) $\dot{p}_r$ becomes positive, (v) $r$ does not evolve more than a part in $10^7$, (vi) $2\Omega$ reaches $\omega_{\textrm{peak}}^{\textrm{NR}}$, (vii) $2M\Omega$ reaches $\pi M f_s$. In order to avoid triggering these stopping conditions at low frequency, where residual orbital eccentricity due to imperfect quasicircular initial conditions could be present, we exploit the $\omega_{\textrm{peak}}^{\textrm{NR}}$ fit to define a radius below which the stopping conditions can be triggered; such threshold value is taken to be $1.5 (\omega_{\textrm{peak}}^{\textrm{NR}}/2)^{-2/3}$.

>>>>

Let us now discuss the construction of the full waveform. The Hamiltonian equations of motion with the above radiation-reaction force are numerically integrated beginning with the quasicircular initial conditions described in Ref.~\cite{Buonanno:2005xu}. The inspiral-plunge waveform is obtained by evaluating Eq.~(\ref{hlminspplunge}) using the solution to the orbital dynamics. Let $\Omega$ be the instantaneous orbital frequency, $r$ be orbital separation, $p_r$ be the radial momentum, $f_s$ be the waveform sampling frequency in Hz, $\omega_{\textrm{peak}}^{\textrm{NR}}$ be the NR fit for the (2,2)-mode amplitude peak of a BNS merger defined in Eq.~(2) of Ref.~\cite{Bernuzzi:2015rla}~\footnote{Note that this fit was tuned to NR simulations only for $0 \leq \kappa_2^T \leq 500$, where $\kappa_2^T$ is defined by Eq.~(1) of Ref.~\cite{Bernuzzi:2015rla}. In our model, for $\kappa_2^T >500$ we use the value of this fit at $\kappa_2^T=500$.}. Then the numerical integration of the orbital dynamics stops when any of the following events happens: (i) $\Omega$ peaks, (ii) $p_r$ becomes positive, (iii) $\dot{r}$ becomes positive, (iv) $\dot{p}_r$ becomes positive, (v) $r$ does not evolve more than a 1000th of the leading-order estimate for $\dot{r}$, that is $\propto 64/5 \nu/r^4$, (vi) $2\Omega$ reaches $\omega_{\textrm{peak}}^{\textrm{NR}}$, (vii) $2M\Omega$ reaches $\pi M f_s$. In order to avoid triggering these stopping conditions at low frequency, where residual orbital eccentricity due to imperfect quasicircular initial conditions could be present, we exploit the $\omega_{\textrm{peak}}^{\textrm{NR}}$ fit to define a radius below which the stopping conditions can be triggered; such threshold value is taken to be $1.5 (\omega_{\textrm{peak}}^{\textrm{NR}}/2)^{-2/3}$.
